Towards End-user Web Scraping For Customization

### 2021-02-14 paper.tex

This type of divide between tasks appears in other domains. In data
science, workflows revolve between cleaning and using data but this
often happens in different environments. The creators of Wrex
\citep{drosos2020}, an end-user programming-by-example system for data
wrangling, reported that ``although data scientists were aware of and
appreciated the productivity benefits of existing data wrangling tools,
having to leave their native notebook environment to perform wrangling
limited the usefulness of these tools.'' This was a major reason Wrex
was developed as an add-on to Jupyter notebooks, the environment in
which data scientists use their data. In web scraping, if a user comes
across an omission while working with data scraped from a website, they
need to switch from the environment in which they are using the data to
the environment in which they created their scraping code in order to
edit and re-run it. This can be seen in many end-user web scraping
systems like Rousillon \citep{chasins2018}and FlashExtract
\citep{le2014} and commercial tools like import.io \citep{zotero-77},
dexi.io \citep{dexi.io}, Octoparse \citep{zotero-83} and ParseHub
\citep{zotero-86}. In web customization, the creators of Vegemite
\citep{lin2009}, a system for end-user programming of mashups, reported
that participants of its user study thought ``it was confusing to use
one technique to create the initial table, and another technique to add
information to a new column.'' This hints at the need for both a unified
environment and a unified workflow.

@@

FlashProg \citep{mayer2015} is a framework that provides user interface
support for FlashExtract \citep{le2014}, a framework for data scraping
by examples. FlashProg's interface provides immediate visual feedback
about the generalization and scrapes the matched values into an output
tab. In addition, it has a program viewer tab that contains a high level
description of what the generated program is doing and provides a list
of alternative programs. Finally, it has a disambiguation tab that
utilizes conversational clarification to disambiguate programs, the
conservations with the user serving as inputs to generate better
programs. Though FlashProg has many desirable features we aim to
implement in future iterations, it does not offer a unified environment
within a browser for scraping and customizing websites.

Rousillon \citep{chasins2018} is a tool that enables end-users to scrape
distributed, hierarchical web data. Its interface does not provide
\emph{full} live feedback about its generalizations or the values to be
scrapped until all the demonstrations have been provided and the
generated program has been run. If run on a website it has encountered
before, Rousillon makes all the previously determined generalizations
visible to the user by color-coding the values on the website that
belong to the same column. This is a desirable feature for our system as
users will not have to actively explore in order to discover which
values are available for scraping and how they are related to each
other. On the extension and repair front, Rousillon presents the web
scraping code generated by demonstration as an editable, high-level,
block-based language called Helena \citep{zotero-51}. While Helena can
be used to perform more complex editing tasks like adding control flow,
it does not support adding or repairing columns after the demonstrations
and presents a change in the model used for creation. Our system
maintains the model used for creation by allowing users to extend and
repair web scraping code via demonstration.

@@

Like existing approaches, web scraping in our current implementation is
limited to what can be demonstrated. This is problematic if users want
to scrape the URL associated with a link element, which is not visible,
or only scrape a substring of a value. To solve this, we plan to harness
Wildcard's formula language. End-users will be able to use formulas
targeted at web scraping to access DOM element properties and
attributes. For example, a formula like
\texttt{=GetAttribute(link\_column,\ ‘href’)} could be used to scrape
URLs of link elements. End-users will also be able to use formulas
targeted at data processing. For example, a formula like
\texttt{=GetSubstring(name\_column,\ 1,\ 2)} could be used to scrape
substrings of text values. Such web scraping and data processing
formulas will give end-users some of the power available to programmers
that write web scraping code in Javascript which supports a wide variety
of DOM access and processing ability.

>>>>

\textless\textless\textless\textless\textless\textless\textless{} HEAD
This type of divide between tasks appears in other domains. In data
science, workflows revolve between cleaning and using data but this
often happens in different environments. The creators of Wrex
\citep{drosos2020}, an end-user programming-by-example system for data
wrangling, reported that ``although data scientists were aware of and
appreciated the productivity benefits of existing data wrangling tools,
having to leave their native notebook environment to perform wrangling
limited the usefulness of these tools.'' This was a major reason Wrex
was developed as an add-on to Jupyter notebooks, the environment in
which data scientists use their data. In web scraping, if a user comes
across an omission while working with data scraped from a website, they
need to switch from the environment in which they are using the data to
the environment in which they created their scraping code in order to
edit and re-run it. This can be seen in many end-user web scraping
systems like Rousillon \citep{chasins2018}and FlashExtract
\citep{le2014} and commercial tools like import.io \citep{zotero-77},
dexi.io \citep{dexi.io}, Octoparse \citep{zotero-83} and ParseHub
\citep{zotero-86}. In web customization, the creators of Vegemite
\citep{lin2009}, a system for end-user programming of mashups, reported
that participants of its user study thought ``it was confusing to use
one technique to create the initial table, and another technique to add
information to a new column.'' This hints at the need for both a unified
environment and a unified workflow. ======= This type of divide between
tasks appears in other domains. In data science, workflows revolve
between cleaning and using data but this often happens in different
environments. The creators of Wrex \citep{drosos2020}, an end-user
programming-by-example system for data wrangling, reported that
``although data scientists were aware of and appreciated the
productivity benefits of existing data wrangling tools, having to leave
their native notebook environment to perform wrangling limited the
usefulness of these tools.'' This was a major reason Wrex was developed
as an add-on to Jupyter notebooks, the environment in which data
scientists use their data. In web scraping, if a user comes across an
omission while working with data scraped from a website, they need to
switch from the environment in which they are using the data to the
environment in which they created their scraping code in order to edit
and re-run it. This can be seen in many end-user web scraping systems
like Rousillon \citep{chasins2018} and commercial tools like import.io
\citep{import.io}, dexi.io \citep{dexi.io}, Octoparse \citep{octoparse}
and ParseHub \citep{parsehub}. In web customization, the creators of
Vegemite \citep{lin2009}, a system for end-user programming of mashups,
reported that participants of its user study thought ``it was confusing
to use one technique to create the initial table, and another technique
to add information to a new column.'' This hints at the need for both a
unified environment and a unified workflow.
\textgreater\textgreater\textgreater\textgreater\textgreater\textgreater\textgreater{}
dff119bf9a1215fb2847215abe2c9722e90542f1

@@

FlashProg \citep{mayer2015} is a framework that provides user interface
support for FlashExtract \citep{le2014}, a framework for data scraping
by examples. FlashProg's interface provides immediate visual feedback
about the generalization and scrapes the matched values into an output
tab. In addition, it has a program viewer tab that contains a high level
description of what the generated program is doing and provides a list
of alternative programs. Finally, it has a disambiguation tab that
utilizes conversational clarification to disambiguate programs, the
conservations with the user serving as inputs to generate better
programs. Though FlashProg has many desirable features we aim to
implement in future iterations, its implementation does not align with
our goal to provide a unified environment within a browser for scraping
and customizing websites.

Rousillon \citep{chasins2018} is a tool that enables end-users to scrape
distributed, hierarchical web data. Because demonstrations can span
across several websites and involve complex data access automtation
tasks, its interface does not provide \emph{full} live feedback about
its generalizations or the values to be scrapped until all the
demonstrations have been provided and the generated program has been
run. If run on a website it has encountered before, Rousillon makes all
the previously determined generalizations visible to the user by
color-coding the values on the website that belong to the same column.
This is a desirable feature for our system as users will not have to
actively explore in order to discover which values are available for
scraping and how they are related to each other. On the extension and
repair front, Rousillon presents the web scraping code generated by
demonstration as an editable, high-level, block-based language called
Helena \citep{zotero-51}. While Helena can be used to perform more
complex editing tasks like adding control flow, it does not support
adding or repairing columns after the demonstrations and presents a
change in the model used for creation. Our system maintains the model
used for creation by allowing users to extend and repair web scraping
code via demonstration.

@@

Like existing programming-by-demonstration approaches, web scraping in
our current implementation is limited to what can be demonstrated. This
is problematic if users want to scrape the URL associated with a link
element, which is not visible, or only scrape a substring of a value. To
solve this, we plan to harness Wildcard's formula language. End-users
will be able to use formulas targeted at web scraping to access DOM
element properties and attributes. For example, a formula like
\texttt{=GetAttribute(link\_column,\ ‘href’)} could be used to scrape
URLs of link elements. End-users will also be able to use formulas
targeted at data processing. For example, a formula like
\texttt{=GetSubstring(name\_column,\ 1,\ 2)} could be used to scrape
substrings of text values. Such web scraping and data processing
formulas will give end-users some of the power available to programmers
that write web scraping code in Javascript which supports a wide variety
of DOM access and processing ability.
